---
title: "ADA Final Project"
author: "Aung Myo Htut"
date: "2022-12-02"
output: html_document
---

```{r}
pacman::p_load(tidyverse, haven, ggplot2, car,table1, broom, lmtest, sjPlot,
               sjmisc, sjlabelled, stargazer,  writeexl)
```

#Import Dataset
```{r}
brfss <- read_xpt("LLCP2018.XPT") %>% select(`_AGE_G`,SEX1,`_IMPRACE`,`INCOME2`,`_EDUCAG`,`_TOTINDA`,EMPLOY1,
      `_BMI5CAT`,SLEPTIM1,DIABETE3)
```

#Rename Variables
```{r}
names(brfss) <- c("Age","Sex","Race/ethnicity","Income","Education Level",
                  "Physical Activity","Employment", "BMI",
                  "Sleep Duration", "Diabetes")
```

#DropNA
```{r}
dim(brfss)
colSums(is.na(brfss))
brfss18 <- brfss %>% drop_na()
colnames(brfss18)
write.csv(brfss18, "brfss18.csv", col.names = TRUE, row.names = FALSE, quote = FALSE)

data <- read_csv("brfss18.csv", show_col_types = FALSE)
dim(data)
```


#Recoding and factoring
```{r, warning=FALSE}
brfss <- read_csv("brfss18.csv", show_col_types = FALSE) %>%
  mutate(Age = factor(Age, levels = 1:6,
                      labels = c("18-24","25-34","35-44","45-54","55-64",">=65")),
         Sex = case_when(Sex==1 ~ 1,
                         Sex==2 ~ 2,
                         TRUE ~ NA_real_),
         Sex = factor(Sex, levels = 1:2,
                      labels = c("Male", "Female")),
         `Race/ethnicity`= case_when(`Race/ethnicity`==1 ~ "NH White",
                                     `Race/ethnicity`==2 ~ "NH Black",
                                     `Race/ethnicity`==3 ~ "NH Asian",
                                     `Race/ethnicity`==4 ~ "NH AI/AN",
                                     `Race/ethnicity`==5 ~ "Hispanic",
                                     `Race/ethnicity`==6 ~ "Other"),
                                     
         Income = case_when(Income%in% c(1,2,3,4) ~1,
                            Income%in%c(5,6) ~2,
                            Income==7 ~ 3,
                            Income==8 ~ 4,
                            TRUE ~ NA_real_),
         Income = factor(Income, levels = 1:4,
                         labels = c("<25k", "25k-<50k", "50k-<75k",">=75k")),
         `Education Level` = case_when(`Education Level`== 1 ~ 1,
                               `Education Level`== 2 ~ 2,
                               `Education Level`== 3 ~ 3,
                               `Education Level`== 4 ~ 4,
                               TRUE ~ NA_real_),
         `Education Level` = factor(`Education Level`, levels = 1:4,
                            labels = c("Did not graduate High School", "Graduated High School",
                                              "Attended College", "Graduated from College")),
         `Physical Activity` = case_when(`Physical Activity`==1 ~ "Yes",
                                         `Physical Activity`==2 ~ "No",
                                         TRUE ~ NA_character_),
         Employment = case_when(Employment%in%c(1,2) ~ 1,
                                Employment%in%c(3,4) ~ 2,
                                Employment%in%c(5,6) ~ 3,
                                Employment==7 ~ 4,
                                Employment==8 ~5,
                                TRUE ~ NA_real_),
         Employment = factor(Employment, levels = 1:5,
                             labels = c("Employed", "Unemployed", "Homemaker/student",
                                        "Retired", "Unable to work")),
         
         BMI = case_when(BMI==1 ~ "Underweight",
                         BMI==2 ~ "Normal Weight",
                         BMI==3 ~ "Overweight",
                         BMI==4 ~ "Obese",
                         TRUE ~ NA_character_),
         `Sleep Duration`= case_when(`Sleep Duration` >=7 & `Sleep Duration`<=9 ~ 1,
                                     `Sleep Duration` <7 ~ 2,
                                     `Sleep Duration` >9 & `Sleep Duration`<= 24 ~ 3,
                                     TRUE ~ NA_real_),
         `Sleep Duration`= factor(`Sleep Duration`,levels = 1:3,
                                  labels = c("Normal sleep", "Short sleep", 
                                             "Long sleep")),
         Diabetes = if_else(Diabetes%in%c(3,4),0,
                            if_else(Diabetes%in%c(1,2),1,NA_real_)),
         Diabetes = factor(Diabetes, levels = 0:1,
                           labels = c("No", "Yes")))
head(brfss)
dim(brfss)
```

#Find Missing Values
```{r}
colSums(is.na(brfss))
```

#Drop NA Values
```{r}
brfss18 <- brfss %>% drop_na()
colSums(is.na(brfss18))
dim(brfss18)
#Percentage of data excluded
100 - nrow(brfss18)/nrow(brfss)*100

```

#Descriptive Statistics - Table 1
```{r}
desc <- table1(~., data = brfss18)
desc

desc1 <- table1 (~ Age + `Race/ethnicity`+ Income + `Education Level`+ 
                   `Physical Activity`+ Employment + BMI + `Sleep Duration`+
                   Diabetes | Sex, data = brfss18)
desc1

desc2 <- table1 (~ Age + Sex +`Race/ethnicity`+ Income + `Education Level`+ 
                   `Physical Activity`+ Employment + BMI + 
                   Diabetes | `Sleep Duration`, data = brfss18)
desc2

#write.xlsx(desc, "table1.xlsx")
```


#Unadjusted Model
```{r}
model1 <- glm(Diabetes~`Sleep Duration`, data = brfss18, family = "binomial")
summary(model1)
tidy(model1, exponentiate = TRUE, conf.int = TRUE) 
```


#Adjusted model
```{r}
model2 <- glm (Diabetes ~ `Sleep Duration`+ Age + Sex + `Race/ethnicity`+ Income+
              `Education Level`+ `Physical Activity`+ Employment + BMI, 
              data = brfss18, 
              family = binomial(link = "logit"))
summary(model2)
broom::tidy(model2, exponentiate = TRUE, conf.int = TRUE)

```


#Model Assumptions of adjusted model
```{r, Assessing Multicolinearity}

#Assessing Multicolinearity
car::vif(model2)

#jtools::summ(model2, vifs = TRUE)
```

No mulitcolinearity between variables as VIF value is less than 10 for all variables.

#Assessing Cook's Distance
```{r}
#Find influential points
plot(model2, which = 4, id.n = 3, col="red")
```
Getting Cook's D Calculations for each observation using augment function from Broom package
```{r}
model2.data <- augment(model2) %>%  
  mutate(index = 1:n()) 

head(model2.data)
```

#Identify and exclude observations with a Cook's Distance greater than a cutoff, use 3 x the mean Cook's D 
```{r}
cuttoff <- mean(model2.data$.cooksd)*3 # defines cutoff variable

brfss_out <- model2.data %>% # excludes observations
  filter(.cooksd<cuttoff)

nrow(brfss_out)/nrow(brfss18) # check percent kept
```

#Fit a model with observations excluded
```{r}
cookmodel <- glm (Diabetes ~ `Sleep Duration`+ Age + Sex + `Race/ethnicity`+ Income+
              `Education Level`+ `Physical Activity`+ Employment + BMI, 
              data = brfss_out, 
              family = binomial(link = "logit"))
summary(cookmodel)
```

Some of the variables in the model becomes not significant after excluding influential observations.

#Compare coefficients between models with and without influential observations
```{r}
compareCoefs(model2, cookmodel)
```

The stand errors are larger in cook model than model 2. That's why I will not exclude influential observations and will proceed with the original data.




#model for effect modification
```{r}
model3 <- glm (Diabetes ~ `Sleep Duration`+ Age + Sex + `Race/ethnicity`+ Income+
              `Education Level`+ `Physical Activity`+ Employment + BMI + 
              `Sleep Duration`*Sex , data = brfss18, 
               family = binomial(link = "logit"))
summary(model3)

#test effect modification with LRT
lrtest(model2, model3)
```


#95% CI for effect modification model
```{r}
broom::tidy(model3, exponentiate = TRUE, conf.int = TRUE) %>% select (-statistic)
```

#Male Only Model
```{r}
malemodel <- glm (Diabetes ~ `Sleep Duration`+ Age + `Race/ethnicity`+ Income+
                 `Education Level`+ `Physical Activity`+ Employment + BMI, 
                 data = brfss18, 
                 family = binomial(link = "logit"), 
                 subset = Sex== "Male")
summary(malemodel)
```

#95% CI for male only model
```{r}
broom::tidy(malemodel, exponentiate = TRUE, conf.int = TRUE) %>% select (-statistic)
```

#Female Only Model
```{r}
femalemodel <- glm (Diabetes ~ `Sleep Duration`+ Age + `Race/ethnicity`+ Income+
                 `Education Level`+ `Physical Activity`+ Employment + BMI, 
                 data = brfss18, 
                 family = binomial(link = "logit"),
                 subset = Sex== "Female")
summary(femalemodel)
```

#95% CI for female only model
```{r}
broom::tidy(femalemodel, exponentiate = TRUE, conf.int = TRUE) %>% select (-statistic)
```

#Combining regression results
```{r}
tab_model(model3, malemodel,femalemodel, show.ci = 0.95, p.val = "wald",
          p.style = "stars", show.p = TRUE, 
          dv.labels = c("Model 1", "Model 2", "Model 3"),
          show.reflvl = FALSE, show.stat = FALSE)
```
